---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = 'man/figures/README-')
```

> [!NOTE]
> ### Superseded by [`causaldata`](https://cran.r-project.org/package=causaldata)
> This package was an early community effort created in 2018 to make datasets from Scott Cunningham's then-unpublished draft of *Causal Inference: The Mixtape* accessible in R (when materials were Stata-only).
> 
> With the official publication of the book, this package has been superseded by the CRAN package [**`causaldata`**](https://cran.r-project.org/package=causaldata) (maintained by Nick Huntington-Klein). For current work with the published textbook, please install `causaldata`:
> 
> ```r
> install.packages("causaldata")
> ```

## Overview

This package provides the datasets used in the book *Causal Inference: The Mixtape* by Scott Cunningham.

## Installation

```{r install, eval = F}
devtools::install_github('johnson-shuffle/mixtape')
```

## Datasets

The datasets included in this package are:

```{r datasets, echo = F}
x <- list.files('data')
x <- gsub('\\.rda', '', x)
```

```{r datasets-list, echo = F, results = 'asis'}
cat(paste('-', x), sep = '\n')
```

See the documentation files for more information.

## Usage

Loading the package attaches each of the datasets into the current environment.

```{r usage}
library(mixtape)

summary(acemogluetal)
```
